\section{Experiment Setup}\label{ch:Research-setup}
This section describes the main experiment conducted to evaluate both analyses.

The configurable system we analyze is the open-source software system \textsc{XZ}, a command-line tool written in \textsc{C} and a component of
\textsc{XZ Utils}\footnote{Visited at 02.04.2023\\ \url{https://tukaani.org/xz/}}.  
The primary compression algorithm that \text{XZ} currently uses to perform lossless data compression is LZMA2.
We use \textsc{XZ} \textsc{(XZ Utils)} version 5.5.0\footnote{Commit hash "610dde15a88f12cc540424eb3eb3ed61f3876f74"}.

The file we compress is a geographic map encoded as a \textsc{JSON} file of size 203 MB\footnote{Visited at 03.04.2023\\ \url{https://github.com/simonepri/geo-maps/releases/latest/download/countries-land-1m.geo.json}},
which we choose because \textsc{XZ} achieves a compression rate of at least $70\%$. 
This ensures that for a file of 203 MB, a significant amount of time is spent in each feature and feature interaction we want to measure.

\subsection{Configuration Space}
%Why config space an features we are interested in
Due to the challenge of combinatorial explosion explained in \autoref{section:combinatorial-explosion}, 
we have to select a subset of features \textsc{XZ} offers to measure all possible configurations 
and ensure the accuracy of the black-box analysis. 

%All features we look at
We selected three core features of \textsc{XZ} that the documentation says to have a significant influence on the system's performance: 
two numeric features, \emph{compression level} and \emph{threads}, and one binary feature, \emph{extreme}. 
The value of \emph{compression level} ranges between \emph{0} and \emph{9} whereas \emph{threads} can either be \emph{0, 1, 2, 4} or \emph{8}. 
%Compression
The feature \emph{compression level} sets the compression preset level, which influences the compression ratio.
This increases the necessary memory needed during compression and decompression, as well as the compression speed. 
This feature is encoded as an alternative group.
%extreme
When \emph{extreme} is enabled \textsc{LZMA} uses a slower variant of the selected compression preset to achieve a potentially better compression ratio.
This feature is optional.
%threads
The feature \emph{threads} specifies the number of worker threads to use, whereas option $0$ makes \textsc{XZ}  use as many threads as available cores.
Multithreading allows \emph{XZ} to split the input into different blocks and compress them independently of one another.
This feature is optional, and encoded as an alternative group.

%Feature Model

The number of configurations we can build using these three features is calculated as follows:

\begin{align}
    \lvert C \rvert &= \lvert \textit{compression level} \rvert \cdot \lvert \textit{extreme} \rvert \cdot \lvert \textit{threads} \rvert \\
    100 &= 10 \cdot 2 \cdot 5 \nonumber
\end{align}

Here $\lvert \textit{compression level} \rvert$, $\lvert \textit{extreme} \rvert$, and $\lvert \textit{threads} \rvert$ are the number of 
configuration options for the respective feature.

To identify the \emph{Base} feature for \textsc{XZ}, we need to identify the time spent in compression independent of which features are selected. 
However, \textsc{XZ} does not allow us to select the mode compression without choosing a compression level. 
Therefore, as the \emph{Base} feature, we choose the configuration with minimal time spent compressing, 
which is \emph{compression level 0} and \emph{threads 0}.