%*******************************************************
% Abstract
%*******************************************************
%\renewcommand{\abstractname}{Abstract}
\pdfbookmark[1]{Abstract}{Abstract}
% \addcontentsline{toc}{chapter}{\tocEntry{Abstract}}
\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Abstract}
Nearly all modern software systems are configurable. To give the end-user flexibility, each system includes various configuration options.
However, it is not clear to the end-user how these configuration options might interact and influence properties such as performance. 

We are interested in whether a change in behavior is the result of single independent configuration options or due to these options 
interacting with each other. In previous research, two different methods have emerged for identifying these influences: 
black-box analysis and white-box analysis. 
We are interested in how accurately these two analysis methods can identify the influences of each configuration option and their interactions. 
To present these influences, we use {\perfInfluenceModel}s and build a model for each analysis out of the data 
they produce. 
We use these {\perfInfluenceModel}s as the foundation for comparing and identifying the differences between white-box and black-box analyses.

In this thesis, we analyze 5 different configurable software systems designed by us and the compression tool \textsc{XZ} using both white-box analysis
and black-box analysis. We present a structured approach to comparing white-box and black-box analyses. 
We could confirm that systems containing multicollinearity leads to inaccurate results for both analyses. 
In addition, the white-box analysis could not identify most configuration options for \textsc{XZ}.
\vfill

\endgroup

\vfill
